---
title: "README"
author: "Tao Sun"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
```


Random Forest model turns out to be the better model for prediction, and it can achieve an accuracy of 60% with optimal parameters here. 

The analysis for [Monday is available here](MondayAnalysis.md).
The analysis for [Tuesday is available here](TuesdayAnalysis.md).
The analysis for [Wednesdayu is available here](WednesdayAnalysis.md).
The analysis for [Thursday is available here](ThursdayAnalysis.md).
The analysis for [Friday is available here](FridayAnalysis.md).
The analysis for [Saturday is available here](SaturdayAnalysis.md).
The analysis for [Sunday is available here](SundayAnalysis.md).

The project [Rmd file is here](ST558project2.Rmd)


```{r automation, eval=TRUE}
# To produce md output automatically
# Create weekday parameter
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

# Create empty vector holders 
for (i in weekdays) {assign(i , rep(0 ,7))}

# Create summary dataset
if (!exists("resultSummary")) {
resultSummary <- dplyr::as_tibble(matrix(0, ncol=7,nrow=7,
                  dimnames = list(c("Total records #", "Training records #", 
                                    "Testing records #", "Features # in LR",
                                    "Prediction accuracy of LR", 
                                    "mTry in RF", 
                                    "Prediction accuracy of RF"),
                          c("Monday", "Tuesday", "Wednesday",
                            "Thursday", "Friday","Saturday", "Sunday"))), 
                  rownames= NA)  %>% rownames_to_column("Stats") 
}

# Create knitr automation parameter and out file names and put into a tibble
output_file <- paste0(weekdays, "Analysis.md")
params <- lapply(weekdays, FUN = function(x){list(weekday=x)})
reports <- tibble(output_file, params)

# Knit file and create reports automatically
apply(reports, MARGIN=1, 
      FUN=function(x){  # x[[1]] since tibble does not simplify.
        rmarkdown::render(input = "ST558project2.Rmd", output_file = x[[1]],
                          params = x[[2]], clean=FALSE, envir=new.env())
      })

# Collect all weekday data into dataframe.
for (i in weekdays) {
  resultSummary[i] <- i
}
```

# Plot the model fitting parameters.
```{r}
knitr::kable(resultSummary)  # Create table

# plot the prediction accurate rate for different weekday 
plotResult <- resultSummary[c(5,7),] %>%  gather(key="Weekday", value = "Prediction Accuracy", 2:8)

ggplot(data=plotResult, aes(x=Weekday, y=`Prediction Accuracy`, group=Stats)) + 
  geom_line(aes(col=Stats)) +
  geom_point() +
  theme(legend.position = "top")
```

